---

title: "survival analysis"
output: html_document
---

```{r}
#install.packages("randomForestSRC")
#install.packages("pec")
#install.packages("survival")
#install.packages("rms")
#install.packages("party")
#install.packages("gtools")
#install.packages("dplyr")
#install.packages("survminer")
#install.packages("caret")
#install.packages("glmnet")
#install.packages("doParallel")
#install.packages("risksetROC")
#install.packages("ggRandomForests")
#install.packages("mlr")
#install.packages("climbeR")
```

```{r}
library(pec)
library(survival)
library(party)
library(gtools)
library(ggplot2)
library(survminer)
library(dplyr)
library(ranger)
```


```{r}
#dataPath<- "Z:/ildproject-share/final_data"
dataPath <- "C:/Users/Joan/OneDrive/capstone/survival analysis"
train_1 <- read.csv(file=paste(dataPath,'final_train_w_onehot.csv',sep="/"), header=TRUE,sep=",")
test_1 <- read.csv(file=paste(dataPath,'final_test_w_onehot.csv',sep="/"), header=TRUE,sep=",")
```

```{r}
#describe(train)
```

```{r}
#describe(test)
```

```{r}
train_1$ild_status <- as.double(train_1$ild_status)
train_1$censored <- as.logical(as.integer(as.character(train_1$censored)))
train_1$t <- as.integer(train_1$t)
train_1$total_xr <- as.numeric(train_1$total_xr)
train_1$total_ct <- as.numeric(train_1$total_ct)
train_1$total_other <- as.numeric(train_1$total_other)

test_1$ild_status <- as.double(test_1$ild_status)
test_1$censored <- as.logical(as.integer(as.character(test_1$censored)))
test_1$t <- as.integer(test_1$t)
test_1$total_xr <- as.numeric(test_1$total_xr)
test_1$total_ct <- as.numeric(test_1$total_ct)
test_1$total_other <- as.numeric(test_1$total_other)


train2 <- subset(train_1, t>=0 )
test2 <- subset(test_1, t>=0)

```

```{r}
#library(caret)
#library(glmnet)
#library(doParallel)
#library(risksetROC)
library(ggRandomForests)
library(randomForestSRC)
```
```{r}
```


```{r}
#use this after the full model is determined
#train5<- select(train2, -X, - patient_id, - ild_status)
#test5<- select(test2, -X, - patient_id, - ild_status)
```

```{r}
train3 <- train2
train3[30:530] <- lapply(train3[30:530], factor)
train3[19:28] <- lapply(train3[19:28], factor)
train4 <- train3[!is.na(train3$age_at_last_visit),]
train4a <- train4[!is.na(train4$total_nbr_procs),]
# train4b <- train4a[!is.na(train4a$total_nbr_visits),]
train5<- select(train4a, -X, -dataset)
train5$other_low_resp <- ifelse((train5$ccs_desc_Oth.low.resp==1|train5$ccs_desc_Other.lower.respiratory.disease==1),1,0)
train6<-train5[,c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,529)]
train7 <- train6[sample(nrow(train6),5000),]
```


```{r}
test3 <- test2
test3[30:530] <- lapply(test3[30:530], factor)
test3[19:28] <- lapply(test3[19:28], factor)
test4 <- test3[!is.na(test3$age_at_last_visit),]
test4a <- test4[!is.na(test4$total_nbr_procs),]
#test4b <- test4a[!is.na(test4a$total_nbr_visits),]

test5 <- select(test4a, -X, -dataset)
test5$other_low_resp <- ifelse((test5$ccs_desc_Oth.low.resp==1|test5$ccs_desc_Other.lower.respiratory.disease==1),1,0)
test6 <- test5[,c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27)]
test7 <- test6[sample(nrow(test6),5000),]
```

```{r}
rm(train_1)
rm(train2)
rm(train3)
rm(train4)
rm(train4a)

rm(test_1)
rm(test2)
rm(test3)
rm(test4)
rm(test4a)
```


```{r}
#save(train5,file=paste(dataPath,"train5.Rds",sep="/"))
#save(test5,file=paste(dataPath,"test5.Rds",sep="/"))
```

```{r}
#load(file=paste(dataPath,"train5.Rds",sep="/"))
#load(file=paste(dataPath,"test5.Rds",sep="/"))
```

###Running different models

```{r}
## S3 method for class 'rfsrc'
tune(Surv(t, censored)~ ., data=train7,
  mtryStart = ncol(train7) / 2,  
  nodesizeTry = c(1:9, seq(10, 100, by = 5)), ntreeTry = 50,
  stepFactor = 1.25, improve = 1e-3, strikeout = 3, maxIter = 25,
  trace = FALSE, doBest = TRUE)

```


```{r}
rf3 <- ranger(Surv(t, censored) ~ gender + race + ethnicity + age_at_last_visit + length_of_first_visit + length_of_last_visit + avg_length_of_all_visits + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other + cigarettes_yn_2 + pipes_yn_2 + cigars_yn_2 + smoking_tob_use_2, data = train7, num.trees=500, importance="impurity", mtry = 12) 
```
```{r}
#Save the model object!!!
#save(rf3, file=paste(dataPath, "rf3.rds", sep="/"))
```
```{r}
print(rf3)
```

```{r}
importance(rf3)
vi <- data.frame(sort(round(rf3$variable.importance, 4), decreasing = TRUE))
names(vi) <- "importance"
head(vi)
```


```{r}
rf4 <- ranger(Surv(t, censored) ~ gender + race + ethnicity + age_at_last_visit + length_of_first_visit + length_of_last_visit + avg_length_of_all_visits + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other, data = train7, num.trees=500, importance="impurity", mtry = 12) 
```
```{r}
#Save the model object!!!
#save(rf3, file=paste(dataPath, "rf3.rds", sep="/"))
```
```{r}
print(rf4)
```


```{r}
importance(rf4)
vi <- data.frame(sort(round(rf4$variable.importance, 4), decreasing = TRUE))
names(vi) <- "importance"
head(vi)
```

```{r}
rf5 <- ranger(Surv(t, censored) ~ gender + race + ethnicity + age_at_last_visit + length_of_first_visit + length_of_last_visit + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other + other_low_resp, data = train7, num.trees=500, importance="impurity", mtry = 12) 
```
```{r}
#Save the model object!!!
#save(rf3, file=paste(dataPath, "rf3.rds", sep="/"))
```
```{r}
print(rf5)
```

```{r}
require(randomForestSRC)
o<- tune(Surv(t, censored)~ gender + race + ethnicity + age_at_last_visit + length_of_first_visit + length_of_last_visit + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other + other_low_resp, data=train7,
  mtryStart = ncol(train7) / 2,  
  nodesizeTry = c(1:9, seq(10, 100, by = 5)), ntreeTry = 50,
  stepFactor = 1.25, improve = 1e-3, strikeout = 3, maxIter = 25,
  trace = FALSE, doBest = TRUE)

```
```{r}
o
```

```{r}
o2<- tune(Surv(t, censored)~ gender + race + ethnicity + age_at_last_visit + length_of_first_visit + length_of_last_visit + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other +smoking_tob_use_2 +other_low_resp, data=train7,
  mtryStart = ncol(train7) / 2,  
  nodesizeTry = c(1:9, seq(10, 100, by = 5)), ntreeTry = 50,
  stepFactor = 1.25, improve = 1e-3, strikeout = 3, maxIter = 25,
  trace = FALSE, doBest = TRUE)

```
```{r}
o2$rf
```
```{r}
o3<- tune(Surv(t, censored)~ age_at_last_visit, data=train7,
  mtryStart = ncol(train7) / 2,  
  nodesizeTry = c(1:9, seq(10, 100, by = 5)), ntreeTry = 50,
  stepFactor = 1.25, improve = 1e-3, strikeout = 3, maxIter = 25,
  trace = FALSE, doBest = TRUE)
o3$rf
```

```{r}
o4<- tune(Surv(t, censored)~ gender + race , data=train7,
  mtryStart = ncol(train7) / 2,  
  nodesizeTry = c(1:9, seq(10, 100, by = 5)), ntreeTry = 50,
  stepFactor = 1.25, improve = 1e-3, strikeout = 3, maxIter = 25,
  trace = FALSE, doBest = TRUE)
o4$rf
```

```{r}
o5<- tune(Surv(t, censored)~ ethnicity + age_at_last_visit + length_of_first_visit + length_of_last_visit + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other +smoking_tob_use_2 +other_low_resp, data=train7,
  mtryStart = ncol(train7) / 2,  
  nodesizeTry = c(1:9, seq(10, 100, by = 5)), ntreeTry = 50,
  stepFactor = 1.25, improve = 1e-3, strikeout = 3, maxIter = 25,
  trace = FALSE, doBest = TRUE)
o5$rf
```


```{r}
o6<- tune(Surv(t, censored)~  age_at_last_visit + length_of_first_visit + length_of_last_visit + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other +smoking_tob_use_2 +other_low_resp, data=train7,
  mtryStart = ncol(train7) / 2,  
  nodesizeTry = c(1:9, seq(10, 100, by = 5)), ntreeTry = 50,
  stepFactor = 1.25, improve = 1e-3, strikeout = 3, maxIter = 25,
  trace = FALSE, doBest = TRUE)
o6$rf
```


```{r}
o7<- tune(Surv(t, censored)~  age_at_last_visit + length_of_first_visit + length_of_last_visit + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other +other_low_resp, data=train7,
  mtryStart = ncol(train7) / 2,  
  nodesizeTry = c(1:9, seq(10, 100, by = 5)), ntreeTry = 50,
  stepFactor = 1.25, improve = 1e-3, strikeout = 3, maxIter = 25,
  trace = FALSE, doBest = TRUE)
o7$rf
```


```{r}
mod1 <- ranger(Surv(t,censored)~age_at_last_visit + length_of_first_visit + length_of_last_visit + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other +smoking_tob_use_2, data=train7,num.tree=500, mtry=4, min.node.size=4)
```


```{r}
```

```{r}
```


```{r}

#use the model object to predict on test
pred3 <- predict(rf3, data = test6, predict.all=FALSE, type="response", se.method="infjack")
```
```{r}
#use ranger.prediction object to calcualte c=index
pp3 <- predictions(pred3)

sum.chf3 <- apply(pred3$chf, 1, sum)
head(sum.chf3)

#library(Hmisc)
c1 <- rcorr.cens(sum.chf3, Surv(test6$t, test6$censored))
c1

library(risksetROC)
  w.ROC = risksetROC(Stime = test6$t,  
                   status = test6$censored, 
                   marker = pp3[,88], 
                   predict.time = 100, 
                   method = "Cox", 
                   main = paste("OOB Survival ROC Curve at t=100"), 
                   lwd = 3, 
                   col = "red" )

w.ROC$AUC
```

### Cox proportional using the vimp from the ranger forest
```{r}
cox <- coxph(Surv(t, censored)~age_at_last_visit + avg_length_of_all_visits +total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct, data=train6 )
```

```{r}
cx.pred <- predict(cox,test6)

```
```{r}
cindex_validation = concordance.index (cx.pred, surv.time = test6$t,
                                       surv.event=test6$censored, method = "noether")
cx.c1 <- rcorr.cens(cx.pred, Surv(test6$t, test6$censored))
cx.c1

library(risksetROC)
  w.ROC = risksetROC(Stime = test6$t,  
                   status = test6$censored, 
                   marker = pp3[,88], 
                   predict.time = 100, 
                   method = "Cox", 
                   main = paste("OOB Survival ROC Curve at t=100"), 
                   lwd = 3, 
                   col = "red" )

w.ROC$AUC

```

### Second random forest-- this includes lower respiratory diag flag
```{r}
rf4 <- ranger(Surv(t, censored) ~ gender + race + ethnicity + age_at_last_visit + length_of_first_visit + length_of_last_visit + avg_length_of_all_visits + total_nbr_visits + total_nbr_procs + avg_nbr_procs_per_encounter + total_xr +total_ct + total_other + tobacco_pak_per_dy_2 + tobacco_used_years_2 + cigarettes_yn_2 + pipes_yn_2 + cigars_yn_2 + snuff_yn_2 + alcohol_oz_per_wk_2 + iv_drug_user_yn_2 + tobacco_user_2 + smoking_tob_use_2+other_low_resp, data = train8, num.trees=500, importance="impurity") 
```

```{r}
#Save the model object!!!
save(rf4, file=paste(dataPath, "rf4.rds", sep="/"))
```
```{r}
print(rf3)
```
```{r}
importance(rf3)
vi <- data.frame(sort(round(rf3$variable.importance, 4), decreasing = TRUE))
names(vi) <- "importance"
head(vi)
```
```{r}
#use the model object to predict on test
pred3 <- predict(rf3, data = test6, predict.all=FALSE, type="response", se.method="infjack")
```
```{r}
#use ranger.prediction object to calcualte c=index
pp3 <- predictions(pred3)

sum.chf3 <- apply(pred3$chf, 1, sum)
head(sum.chf3)

#library(Hmisc)
c1 <- rcorr.cens(sum.chf3, Surv(test6$t, test6$censored))
c1

library(risksetROC)
  w.ROC = risksetROC(Stime = test6$t,  
                   status = test6$censored, 
                   marker = pp3[,88], 
                   predict.time = 100, 
                   method = "Cox", 
                   main = paste("OOB Survival ROC Curve at t=100"), 
                   lwd = 3, 
                   col = "red" )

w.ROC$AUC
```
```{r}

importance(rf4)
rf2$survival

pp <- predict(rf2, data = test7)
pp1 <- predict(rf2, data = test7, predict.all=FALSE, type="response", se.method="infjack")


table(test7$t,predictions(pp))
#predict on test
pred.test.fin = predict(rf2, 
                         newdata = test7, 
                         importance = "none" )
  c      
c.test <- rcorr.cens(pp1$predictions, 
           Surv(test7$t, test7$censored))["C Index"]

length(predictions(pp1))
length(pp$chf)

surv_prob <- data.frame(pp1$survival)
length(surv_prob)

library(Hmisc)
c1 <- rcorr.cens(predictions(pp1), 
           Surv(test7$t, test7$censored))["C Index"]
c1

zz <- data.frame(predictions(pp1))
length(zz)
z3 <- pp1$survival
z4 <-pp1$prediction
length(z3)
```

```{r}


w.ROC = risksetROC(Stime = test5$t,  
                   status = test5$censored, 
                   marker = pred.test.fin$predicted, 
                   predict.time = 190, 
                   method = "Cox", 
                   main = paste("OOB Survival ROC Curve at t=190"), 
                   lwd = 3, 
                   col = "red" )

w.ROC$AUC
```

```{r}
#Clean up for unnecessary columns-- when using dx info
nas_df <- data.frame(sapply(train5, function(y) sum(length(which(is.na(y))))))

```
```{r}

train5a <- train5[train5$ild_status==1,]
train_df <- data.frame(sapply(train5a[28:528], function(y) sum(length(which((y==1))))))
colnames(train_df) <- c("col1")
newdata <- subset(train_df, col1>50,
select=col1)

train5$other_low_resp <- ifelse((train5$ccs_desc_Oth.low.resp==1|train5$ccs_desc_Other.lower.respiratory.disease==1),1,0)

train_test <- train5[train5$other_low_resp==1,]

```
```{r}
test5a <- test5[test5$ild_status==1,]
test_df <- data.frame(sapply(test5a[28:528], function(y) sum(length(which((y==1))))))
colnames(test_df) <- c("col1")
newdata_a <- subset(test_df, col1>0,
select=col1)
```

```{r}


colnames_df <- data.frame(colnames(train5))

a <- test_df[test_df$col1<100,]


test$fac <- factor(test$fac, levels = levels(train$fac))

rf <- ranger(Surv(t, censored) ~ ., data = train7, num/trees=500, mtry=57) 

colnames(train7)
```


#second model
```{r}
out.rsf.2 <- rfsrc(Surv(t, censored)~ gender + race+ ethnicity+ first_zip_d + age_at_last_visit +length_of_last_visit + avg_length_of_all_visits+total_nbr_visits +total_nbr_procs + avg_nbr_procs_per_encounter+total_xr+total_ct+total_other, data=train5, ntree=200, nsplit=2)
```

```{r}

print(out.rsf.2)
```

```{r}
imp.rsf.2 <- sort(vimp(out.rsf.2)$importance, 
                  decreasing = T)
imp.rsf.2
```
```{r}
plot(gg_vimp(out.rsf.2))
plot(gg_error(out.rsf.2$err.rate))
```

```{r}
length(out.rsf.2$predicted.oob)
```

```{r}
head(out.rsf.2$predicted.oob)

```

```{r}
sum.chf.oob <- apply(out.rsf.2$chf.oob,1,sum)
head(sum.chf.oob)
```

```{r}
c2<- rcorr.cens(out.rsf.2$predicted.oob, 
           Surv(train5$t, train5$censored))["C Index"]
c2
```

```{r}
out.rsf.3 <- rfsrc(Surv(t, censored)~ gender + race+ ethnicity+ first_zip_d + age_at_last_visit +length_of_last_visit + avg_length_of_all_visits+total_nbr_visits +total_nbr_procs + avg_nbr_procs_per_encounter+total_xr+total_ct+total_other, data=train5, ntree=1000, nsplit=2)
```

```{r}
print(out.rsf.3)
```
```{r}
imp.rsf.3 <- sort(vimp(out.rsf.3)$importance, 
                  decreasing = T)
imp.rsf.3
```
```{r}
plot(gg_vimp(out.rsf.3))

```


```{r}
length(out.rsf.3$predicted.oob)

```

```{r}
head(out.rsf.3$predicted.oob)

```

```{r}
sum.chf.oob <- apply(out.rsf.3$chf.oob,1,sum)
head(sum.chf.oob)
```

```{r}
c3 <- rcorr.cens(out.rsf.3$predicted.oob, 
           Surv(train5$t, train5$censored))["C Index"]
c3
```
```{r}
# plot(gg_error(out.rsf.3))
```


```{r}
out.rsf.4 <- rfsrc(Surv(t, censored)~ gender + race+ ethnicity+ first_zip_d + age_at_last_visit +length_of_last_visit + avg_length_of_all_visits+total_nbr_visits +total_nbr_procs + avg_nbr_procs_per_encounter+total_xr+total_ct+total_other, data=train5, ntree=2500, nsplit=2, nodesize=5)
```

```{r}
c4 <- rcorr.cens(out.rsf.4$predicted.oob, 
           Surv(train5$t, train5$censored))["C Index"]
c4
```
```{r}
out.rsf.5 <- rfsrc(Surv(t, censored)~ gender + race+ ethnicity+ first_zip_d + age_at_last_visit +length_of_last_visit + avg_length_of_all_visits+total_nbr_visits +total_nbr_procs + avg_nbr_procs_per_encounter+total_xr+total_ct+total_other, data=train5, ntree=2000, nsplit=2, nodesize=10)
```

```{r}
print(out.rsf.5)
```
```{r}
c5 <- rcorr.cens(out.rsf.5$predicted.oob, 
           Surv(train5$t, train5$censored))["C Index"]
c5
```


```{r}
out.rsf.6 <- rfsrc(Surv(t, censored)~ ., data=train5, ntree=500, nsplit=10, nodesize=9, mtry=30)
```
```{r}
print(out.rsf.6)
```

```{r}
imp.rsf.6 <- sort(vimp(out.rsf.6)$importance, 
                  decreasing = T)
imp.rsf.6
```

```{r}
plot(gg_vimp(out.rsf.6))
```

```{r}
c6 <- rcorr.cens(out.rsf.6$predicted.oob, 
           Surv(train5$t, train5$censored))["C Index"]
c6

```



###Look at the c-indexes

```{r}
rbind(c1,c2,c3,c4,c5 )
```
From the above, plug the best model into the predict function below



```{r}
pred.test.fin = predict(out.rsf.6, 
                         newdata = test5, 
                         importance = "none" )

rcorr.cens(-pred.test.fin$predicted , 
             Surv(test5$t, test5$censored))["C Index"]
```

```{r}
library(risksetROC)

```

```{r}
w.ROC = risksetROC(Stime = train5$t,  
                   status = train5$censored, 
                   marker = out.rsf.1$predicted.oob, 
                   predict.time = median(train5$t), 
                   method = "Cox", 
                   main = paste("OOB Survival ROC Curve at t=", 
                                median(train5$t)), 
                   lwd = 3, 
                   col = "red" )

w.ROC$AUC


```

```{r}

w.ROC = risksetAUC(Stime = train5$t,  
                   status = train5$censored, 
                   marker = out.rsf.3$predicted.oob,
                   tmax = 350)
```
```{r}
w.ROC = risksetAUC(Stime = test5$t,  
                   status = test5$censored, 
                   marker = pred.test.fin$predicted, 
                   tmax = 220, 
                   method = "Cox")

```
```{r}


w.ROC = risksetROC(Stime = test5$t,  
                   status = test5$censored, 
                   marker = pred.test.fin$predicted, 
                   predict.time = 190, 
                   method = "Cox", 
                   main = paste("OOB Survival ROC Curve at t=190"), 
                   lwd = 3, 
                   col = "red" )

w.ROC$AUC
```

```{r}
test5$t[test5$t>2]

```


```{r}

#plot(gg_survival(interval = "days", censor = "ild_status", by = "bili_grp",data = train4), error = "none")
#labs(y = "Survival Probability", x = "Observation Time (years)",color = "Bilirubin")

plot(gg_rfsrc(out.rsf.6, by = train5$censored)) + theme(legend.position = c(0.2, 0.2)) +
 labs(y = "Survival Probability", x = "Time (days)") +
  coord_cartesian(ylim = c(-0.5, 1.01))
```
```{r}
cols <- c("red", "blue")

ggRFsrc <- plot(gg_rfsrc(out.rsf.6), alpha = 0.2) +
  scale_color_manual(values = cols) +
  theme(legend.position = c(0.2,0.2 )) +
  labs(y = "Survival Probability", x = "Time (days)") +
  coord_cartesian(ylim = c(-0.01, 1.01))
show(ggRFsrc)

#ggsurvplot(out.rsf.3, data =train5, pval = TRUE)
```


```{r}
plot(gg_rfsrc(pred.test.fin), alpha=.2) + scale_color_manual(values=cols)+
  theme(legend.position=c(0.2,0.2 ))+ labs(y="Survival Probability", x="Time (days)"+
                                        coord_cartesian(ylim=c(-0.01, 1.01)))
```

```{r}
gg_v <- gg_variable(out.rsf.3, time = c(50, 100),
                   time.labels = c("50 days", "100 days"))

plot(gg_v, xvar = "ILD_status", alpha = 0.4) + #, se=FALSE
+ labs(y = "Survival", x = train5$censored["TRUE"]) +
ggRandomForests + theme(legend.position = "none") +
R+ scale_color_manual(values = cols, labels = event.labels) +
R+ scale_shape_manual(values = event.marks, labels = event.labels) +
R+ coord_cartesian(ylim = c(-0.01, 1.01))

```

```{r}
head(app)
plot(app[1,21:49])
```

```{r}
# ranger model
#r_fit <- ranger(Surv(time, status) ~ trt + celltype + 
                   #  karno + diagtime + age + prior,
                    # data = vet,
                    # mtry = 4,
                    # importance = "permutation",
                    # splitrule = "extratrees",
                    # verbose = TRUE)


# Average the survival models
death_times <-pred.test.fin$time.interest 
surv_prob <- data.frame(pred.test.fin$survival)
avg_prob <- sapply(surv_prob,mean)

# Plot the survival models for each patient
plot(pred.test.fin$time.interest, pred.test.fin$survival[137,], 
     type = "l", 
     ylim = c(0,1),
     col = "red",
     xlab = "Days",
     ylab = "survival",
     main = "Patient Survival Curves")

#
#cols <- colors()
#for (n in sample(c(2:dim(test5)[1]),10)){
 # lines(out.rsf.3.test$time.interest, out.rsf.3.test$survival[n,], type = "l", col = cols[n])
#}
#lines(death_times, avg_prob, lwd = 2)
#legend(500, 0.7, legend = c('Average = black'))
```


```{r}
out.rsf.4 <- rfsrc(Surv(t, censored)~ gender + race+ ethnicity+ first_zip_d + age_at_last_visit +length_of_last_visit + avg_length_of_all_visits+total_nbr_visits +total_nbr_procs + avg_nbr_procs_per_encounter+total_xr+total_ct+total_other, data=train5, ntree=5, nsplit=2)
```

```{r}
print(out.rsf.4)
```

```{r}
pred.test.fin = predict(out.rsf.4, 
                         newdata = test5, 
                         importance = "none" )

rcorr.cens(-pred.test.fin$predicted , 
             Surv(test5$t, test5$censored))["C Index"]
```


```{r}
#install.packages("Hmisc")
require(Hmisc)
```

```{r}
rcorr.cens(out.rsf.4$predicted.oob, 
           Surv(train5$t, train5$censored))["C Index"]
#200, 5, 0.32
#15, 5, 0.4
#25,2, 0.36
#10,2, 0.436
```


```{r}
imp.rsf.2 <- sort(vimp(out.rsf.2)$importance, 
                  decreasing = T)
imp.rsf.2
```
```{r}
plot(gg_vimp(out.rsf.2))

plot(gg_error(out.rsf.2$err.rate))
```
```{r}
out.rsf.2$err.rate
```

```{r}
length(out.rsf.2$predicted.oob)
```

```{r}
head(out.rsf.2$predicted.oob)

```

```{r}
sum.chf.oob <- apply(out.rsf.2$chf.oob,1,sum)
head(sum.chf.oob)
```





```{r}

out.rsf.3.test$time.interest

out.rsf.3.test$survival
```
### Cox regression
```{r}
res.cox <- coxph(Surv(t, censored)~ gender + race+ ethnicity+ first_zip_d + age_at_last_visit +length_of_last_visit + avg_length_of_all_visits+total_nbr_visits +total_nbr_procs + avg_nbr_procs_per_encounter+total_xr+total_ct+total_other, data=train5)

summary(res.cox)
```

```{r}
pred.test.fin.a = predict(res.cox, 
                         newdata = test5, 
                         importance = "none" )

rcorr.cens(pred.test.fin.a$predicted , 
             Surv(test5$t, test5$censored))["C Index"]

```
```{r}
pred.test.fin.a$predic
```


```{r}
ggsurvplot(fit, conf.int = TRUE, palette = "Dark2", 
           censor = FALSE, surv.median.line = "hv")
```
ggsurvplot(fit, conf.int = TRUE, legend.labs=c("Sex=1", "Sex=2"),
           ggtheme = theme_minimal())
```
```{r}
# Plot the baseline survival function
#ggsurvplot(survfit(res.cox), color = "#2E9FDF",
           ggtheme = theme_minimal())
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```


```{r}
library(survminer)
require(survival)
ggsurvplot(out.rsf.3,data=test5)
```


```{r}
plot(out.rsf.3$survival.oob, mark.time=F)
```


```{r}
```



```{r}
surv_object <- Surv(time=train4[0:5000,]$t, event=train4[0:5000,]$censored)
```

```{r}
cox_model <- survfit(surv_object
~ gender + race+ ethnicity + first_zip_d +age_at_last_visit + total_nbr_visits +total_nbr_procs +total_ct + total_other, data=train4[0:5000,])
```

```{r}
summary(cox_model)
```
```{r}
cox_fit<- survfit(cox_model)

```

```{r}
plot(cox_fit, main = "cph model", xlab="Days")

```

```{r}
ggsurvplot(cox_fit, data =train4, pval = TRUE)


```

```{r}
summary(train4$gender)
```
```{r}
glimpse(train4)

```

```{r}
a<-selectCox(fitform, data=train4, rule="aic")
a
print(a$fit)

```

```{r}
fitrsf <- rfsrc(fitform,data=train4)
```

```{r}
fitrsf
```
```{r}
prsf <- predictSurvProb(fitrsf, newdata=test, times=t)

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

